Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-22 Ch1_movement_rates/Ch1_Figures.Rmd
just added a comment

dist_range <- c(1000, 5000, 10000)
pextRemes(fit, dist_range, lower.tail = FALSE)

>>>>

# To find the probability of exceeding 1000, 5000, or 10,000 meters based on the fitted ged 
dist_range <- c(1000, 5000, 10000)
pextRemes(fit, dist_range, lower.tail = FALSE)

# Not sure this is right though. I want the conditional probability that a dispersal distance that is already over the threshold goes beyong 1000, 5000, and 10000 meters.
